The Impact of Educational Expenses of New Coders

### 2021-04-20 outputs/paper/paper.Rmd
Edit model equations
Add regression model for city population

## Model formulae

@@

\begin{equation}
(\#eq:linRegModel1)
MoneyForLearning \sim \beta_0 + \beta_1 \times CityPopulation + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel2)
MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel3)
MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
\end{equation}

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Multiple regression analysis ####
multiReg1 <- lm(formula = 
               MoneyForLearning ~ 
               CityPopulation +
               # CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

multiReg2 <- lm(formula = 
               MoneyForLearning ~ 
               Age +
               CityPopulation +
               # CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

@@

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Result of regression model", 
          header = FALSE,
          type = "latex")
```

>>>>

## Model Formulae

@@

\begin{equation}
(\#eq:linRegModel1)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel2)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel3)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
\end{equation}

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Multiple regression analysis ####

### Run linear regression models
multiReg1 <- lm(formula = 
               MoneyForLearning ~ 
               Income,
               data = dfNewCoders)

multiReg2 <- lm(formula = 
               MoneyForLearning ~ 
               # Gender +
               # Age +
               CityPopulation +
               # CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

@@

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Predictions of money for learning across experimental conditions", 
          header = FALSE,
          type = "latex")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Multiple regression analysis (by city population) ####
dfSmCity <-
  dfNewCoders %>%
  filter(CityPopulation == 0)

dfMdCity <-
  dfNewCoders %>%
  filter(CityPopulation == 1)

dfLgCity <-
  dfNewCoders %>%
  filter(CityPopulation == 2)

### Run linear regression models
linReg1 <- lm(formula = 
               MoneyForLearning ~ 
               Income,
               data = dfNewCoders)

linReg2 <- lm(formula = 
               MoneyForLearning ~ 
               Income,
               data = dfSmCity)

linReg3 <- lm(formula = 
               MoneyForLearning ~ 
               Income,
               data = dfMdCity)

linReg4 <- lm(formula = 
               MoneyForLearning ~ 
               Income,
               data = dfLgCity)

stargazer::stargazer(linReg1, linReg2, linReg3, linReg4,
          title = "Predictions of money for learning by city population", 
          header = FALSE,
          type = "latex",
          column.labels = c("Any", "Small", "Medium", "Large"),
          font.size = "tiny")
